Management induced changes of soil organic carbon on global croplands

### 2020-11-09 ResultNotebooks/results_SOCcompare.Rmd
update with spell check, references for discussion part, additional analysis on initialization, update of figures

rev       <- "rev0.76baseline"
outputdir <- "Output/"

@@

```{r plot reg stock, out.width="100%", out.height=1000}

library(mip)
library(quitte)
library(ggplot2)

getNames(reg_SOCStock) <- paste0("modeloutput.SOCbudget.", getNames(WISE,dim=3))
getSets(reg_SOCStock)  <- getSets(WISE)

hist <- rbind(as.quitte(WISE["GLO",,,invert=TRUE]),
              as.quitte(GSOC["GLO",,,invert=TRUE]),
              as.quitte(SoilGrids["GLO",,,invert=TRUE]),
              as.quitte(LPJ_rev21["GLO",,,invert=TRUE][,,2]))

regSOCcompare <- mipLineHistorical(reg_SOCStock, hist, facet.ncol=4, scales="free_y", ylab="SOC (0-30cm) in MtC")

ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid)
```

```{r bar plot}

### FROM ISABELLE

# p.tc <- ggplot() 
# # agass Hauptszenarien --> Balken
# p.tc <-p.tc + geom_bar(data = dat1a, aes(x = Region, y = Value, fill=Mainscen,group=factor(Mainscen)),stat = "identity",width = 0.7,position=position_dodge(0.7),alpha=0.8, show_guide=FALSE) 
# p.tc <- p.tc + scale_fill_manual(values = c("#999999","#FF3300","#66CC00","#3366FF"),breaks=c("baseline","S1a","S3a","S3c"),
#                                  labels=c("Baseline     ","Climate_impacts     ","Shift_to_rangeland     ","Shift_to_mixed     "))
# # agass mit co2 --> graue K?stchen
# p.tc <- p.tc + geom_point(data=dat2a,aes(x = Region, y = Value, group=factor(Mainscen)),size=4,position=position_dodge(0.7),colour="black",shape=22,fill="grey")
# 
# # Spread GCMs ohne co2
# p.tc <- p.tc + geom_errorbar(data=dat4a,aes(x = Region, ymin = min,ymax=max, group=Mainscen),position=position_dodge(0.7),width=.2,colour="dark red", linetype="dashed",size=0.6,show_guide=FALSE)
# #p.tc <- p.tc + geom_point(data=dat3a,aes(x = Region, y = Value, group=factor(Mainscen)),size=1.5,position=position_dodge(0.7),colour="red", show_guide=FALSE)
# p.tc <- p.tc + geom_point(data=dat4a,aes(x = Region, y = min, group=factor(Mainscen)),size=3.8,position=position_dodge(0.7),colour="dark red",shape=21,fill="white", show_guide=FALSE)
# p.tc <- p.tc + geom_point(data=dat4a,aes(x = Region, y = max, group=factor(Mainscen)),size=2.5,position=position_dodge(0.7),colour="dark red",shape=19, show_guide=FALSE)
# 
# # Spread GCMs mit co2
# p.tc <- p.tc + geom_errorbar(data=dat4b,aes(x = Region, ymin = min,ymax=max, group=Mainscen),position=position_dodge(0.7),width=.2,colour="#003300",size=0.6, show_guide=FALSE)
# #p.tc <- p.tc + geom_point(data=dat3b,aes(x = Region, y = Value, group=factor(Mainscen)),size=1.5,position=position_dodge(0.7),colour="#003300", show_guide=FALSE)
# p.tc <- p.tc + geom_point(data=dat4b,aes(x = Region, y = min, group=factor(Mainscen)),size=3.5,position=position_dodge(0.7),colour="#003300",shape=23,fill="white", show_guide=FALSE)
# p.tc <- p.tc + geom_point(data=dat4b,aes(x = Region, y = max, group=factor(Mainscen)),size=3.8,position=position_dodge(0.7),colour="#003300",shape=18, show_guide=FALSE)
# 
# #Layout
# p.tc <- p.tc + labs(y="Average annual TC rates 2005-2045 [%] \n",x="")
# guides(colour = guide_legend(override.aes = list(shape = NA)))
# p.tc <- p.tc + geom_hline(yintercept=0)
# 
# #p.tc <- p.tc + ylim(0, 2.4)
# p.tc <- p.tc + theme_bw() +
#   theme(axis.text = element_text(size = 16,face="bold"),
#         axis.title = element_text(size = 18,face="bold"),
#                 
#         legend.background = element_rect(fill = "white",colour="black",size=0.7),
#         legend.text =       element_text(size = 14, face="bold"),
#         legend.title =      element_blank(),
#         legend.position = c(0.25, 1.01),
#         legend.key = element_rect(colour = "white",size=2),
#         legend.key.height = unit(0.7,"cm"),
#         legend.key.width = unit(1.8,"cm"),
#         legend.margin = unit(100,"lines"),
#         
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         
#         panel.border = element_rect(size = 0.8, colour = "black"),
#         plot.margin = unit(c(0.5,0.5,0.5,0.5),"cm")  # top, right, bottom, and left margins
#   )
# 
# #Legend 1
# p.tc <- p.tc + annotate("rect", xmin = 0.6, xmax = 4.5, ymin = 2.3, ymax = 3.3,fill = "white",colour="black",size=0.7)
# 
# p.tc <- p.tc + annotate("text", x = 0.8, y = 3.1, label = "IAASTD~climate~scenario~w/o~CO[2]~effect",parse = TRUE,size = 4.7, hjust=0)
# 
# p.tc <- p.tc + annotate("text", x = 1.8, y = 2.9, label = "climate_impacts",size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("rect", xmin = 0.8, xmax = 1.6, ymin = 2.85, ymax = 2.95,fill = "#FF3300",size=0.7)
# 
# p.tc <- p.tc + annotate("text", x = 1.8, y = 2.7, label = "shift_to_rangeland",size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("rect", xmin = 0.8, xmax = 1.6, ymin = 2.65, ymax = 2.75,fill = "#66CC00",size=0.7)
# 
# p.tc <- p.tc + annotate("text", x = 1.8, y = 2.5, label = "shift_to_mixed",size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("rect", xmin = 0.8, xmax = 1.6, ymin = 2.45, ymax = 2.55,fill = "#3366FF",size=0.7)
# 
# 
# #Legend 2
# p.tc <- p.tc + annotate("rect", xmin = 7.6, xmax = 11.4,  ymin = 2.3, ymax = 3.3,fill = "white",colour="black",size=0.7)
# 
# p.tc <- p.tc + annotate("text", x = 9, y = 3.0, label = "full~CO[2]~effect~(IAASTD)",parse = TRUE, size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("point", x = 8.4, y = 3.0, colour="black",shape=22,fill="grey",size=4.5)
# 
# p.tc <- p.tc + annotate("text", x = 9, y = 2.8, label = "full~CO[2]~effect~(all~GCMs)",parse = TRUE, size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("segment", x = 8, xend=8.8, y = 2.8, yend=2.8,colour="#003300",size=0.7)
# p.tc <- p.tc + annotate("point", x = 8, y = 2.8, colour="#003300",shape=23,fill="white",size=3.8)
# p.tc <- p.tc + annotate("point", x = 8.8, y = 2.8, colour="#003300",shape=18,size=5)
# 
# p.tc <- p.tc + annotate("text", x = 9, y = 2.6, label = "w/o~CO[2]~effect~(all~GCMs)",parse = TRUE,size = 4.7, hjust=0)
# p.tc <- p.tc + annotate("segment", x = 8, xend=8.8, y = 2.6, yend=2.6,colour="dark red",linetype="dashed",size=0.7)
# p.tc <- p.tc + annotate("point", x = 8, y = 2.6, colour="dark red",shape=21,fill="white",size=4)
# p.tc <- p.tc + annotate("point", x = 8.8, y = 2.6, colour="dark red",shape=19,size=4)
# 
# 
# print(p.tc)

@@

>>>>

rev       <- "rev0.76baseline"
outputdir <- "Output/Images/"

@@

```{r point plot reg stock, out.width=800, out.height=600}
library(ggplot2)

leg_name <- "Data Source"

glob <- ggplot(data = as.data.frame(glo_SOC["GLO",,][,"y2010",]/1000), aes(Year,Value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  scale_size_manual(values=c(4,2,2,2,2)) + 
  scale_shape_manual(values=c(19,6,2,5,0)) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC")

comp <- ggplot(data = as.data.frame(glo_SOC["GLO",,invert=TRUE][,"y2010",]/1000), aes(Year,Value, group=Data1)) + 
  geom_point(aes(colour=Data1, size=Data1, shape=Data1)) + 
  facet_wrap(~ Region, scales="free", drop=TRUE) + 
  scale_size_manual(values=c(4,2,2,2,2)) + 
  scale_shape_manual(values=c(19,6,2,5,0)) +
  labs(color  = leg_name, size = leg_name, shape = leg_name) +
  xlab("") + ylab("SOC (0-30cm) in GtC")

glob
comp

ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob, height=6, width=3, units="cm")
ggsave(paste0(outputdir,"/reg_comparisonfigure.png"), plot=comp)

@@

```{r point plot glo stock, fig.width=3, fig.height=4}
library(ggplot2)

glob
ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob)
```

### 2020-11-09 ResultNotebooks/results_SOCsceninit.Rmd
update with spell check, references for discussion part, additional analysis on initialization, update of figures

rev <- "rev0.76baseline"

@@

#revisions   <- c(Baseline="rev0.74baseline", Till="rev0.74tillage_mixedtill", ResRe="rev0.74residue_freeze1975", ManRe="rev0.74manure_freeze1975", Yield="rev0.74yield_freeze1975")
filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

revisions   <- c(Baseline="rev0.76baseline", Allon="rev0.76allon_freeze1975", Allon2="rev0.76allon2_freeze1975",        ResRe="rev0.76rrecycle_freeze1975",
                Till="rev0.76tillage_mixedtill", ResSta="rev0.76residue_freeze1975", Yield="rev0.76yield_freeze1975", ManRe="rev0.76manure_freeze1975")

@@

plot_rev <- c(5,8,6,3)

names(revisions) <- c("Historical Management", 
                      "Allon",    
                      "Constant management from 1975",   
                      "ResRe", 
                      "Constant tillage area from 1975",
                      "Constant residue input from 1975",
                      "Yield", 
                      "Constant manure application from 1975")

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),c(1,plot_rev)]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC gap in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = c(-44,-36),
                     breaks = c(-36, -38, -40,- 42, -44)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size))

@@

ggsave(paste0(outputdir,"/scenario.png"), plot=SOCemis)

>>>>

rev <- "rev0.77init_lu"

@@

revisions   <- c(InitLu="rev0.77init_lu", InitNv="rev0.77init_natveg", InitMix="rev0.77init_mixed")
filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

@@

plot_rev <- c(2,3)

names(revisions) <- c("steady state of land use","steady state of potential natural vegetation","mean of steady states above")

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,1),c(1,plot_rev)]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC gap in GtC",
        color="Initilization of SOC stocks in 1960 by") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = c(-45,-0),
                     breaks = seq(-45,0,5)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size))

@@

ggsave(paste0(outputdir,"/scenario_lu.png"), plot=SOCemis)

### 2020-11-09 SOCbudgetPaper/SOCbudget.Rmd
update with spell check, references for discussion part, additional analysis on initialization, update of figures

---
title: Management induced changes of soil organic carbon on global croplands 
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: |
  Soil organic carbon (SOC) is one of larges carbon stocks on Earth. It is three times larger than the biospheric pool and more than twice as big as the athmospheric pool, when looking into the first meter of the earth soil profile. Human cropping activties led and still lead to a depletion of SOC though, which are so far not well represented in global assessments of historic carbon emissions. While SOC models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these biophysical processes are still little investigated on the global scale. Here we create a spatial explicit data set for agricutural management on cropland, especially for crop residue and manure management, based on global historic production (FAOSTAT), and land-use (LUH2) data; and combine it with the IPCC Tier 2 approach to create a half degree resolution SOC stock changes on mineral soils. We estimate that due to arable farming soils have lost over 37 GtOC of which 4 GtOC have been regained within the period 1975-2010. We show that, our results on global scale based on Tier 2 IPCC methodolgy are in good agreement with Tier 1 default assumptions. We also find that SOC is very sensitive to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models.
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/. Data used for the output can be found under <something-with-zenodo>.  
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky (and <here_could_be_your_names>). 
  Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
output:
  rticles::copernicus_article: default
  md_document:
    variant: markdown_github
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  bookdown::word_document2: default
  bookdown::pdf_document2: default
---
\newpage

>>>>

---
title: Management induced changes of soil organic carbon on global croplands 
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: |
  Soil organic carbon (SOC) is one of larges carbon stocks on Earth. It is three times larger than the vegetation pool and more than twice as big as the athmospheric pool, when looking into the first meter of the earth soil profile. Human cropping activties led and still lead to a depletion of SOC though, which are so far not well represented in global assessments of historic carbon emissions. While SOC models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these biophysical processes are still little investigated on the global scale. Here we create a spatial explicit data set for agricutural management on cropland, especially for crop residue and manure management, based on global historic production (FAOSTAT), and land-use (LUH2) data; and combine it with the IPCC Tier 2 approach to create a half degree resolution SOC stock changes on mineral soils. We estimate that due to arable farming soils have lost over 37 GtOC of which 4 GtOC have been regained within the period 1975-2010. We show that, our results on global scale based on Tier 2 IPCC methodolgy are in good agreement with Tier 1 default assumptions. We also find that SOC is very sensitive to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models.
bibliography: SOCbudget2.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/. Data used for the output can be found under <something-with-zenodo>.  
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky (and <here_could_be_your_names>). 
  Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
output:
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  md_document:
    variant: markdown_github
  bookdown::word_document2: default
  rticles::copernicus_article: default
  bookdown::pdf_document2: default
---
\newpage
